Title

### 2017-05-09 paper/paper.tex
Filled out initial implementation sections and added convenient Makefile for auto-LaTeX-ing from the command line.

\begin{enumerate}
	\item We read the paper \textit{Rawlsian Fairness for Machine Learning}  \cite{DBLP:journals/corr/JosephKMNR16}.
	\item We implemented the TopInterval, IntervalChaining, and RidgeFair algorithms from the paper in Python. 
	\item We ran our implementations on a Yahoo! dataset containing a fraction of the user click log for news articles displayed in the Featured Tab of the Today Module on the Yahoo! Front Page during the first ten days in May 2009 \cite{yahoo}, to see how well they performed on real data.
	\item To empirically evaluate our implementations, we ran experiments similar to those in \cite{DBLP:journals/corr/JosephKMNR16} with randomly-drawn contexts. 
	\item We compiled our findings into a written report.
\end{enumerate}

@@

@@

@@

@@

>>>>

\begin{enumerate}
	\item We read the paper \textit{Rawlsian Fairness for Machine Learning}  \cite{DBLP:journals/corr/JosephKMNR16}.
	\item We implemented the \texttt{TopInterval}, \texttt{IntervalChaining}, and \texttt{RidgeFair} algorithms from the paper in Python. 
	\item We ran our implementations on a Yahoo! dataset containing a fraction of the user click log for news articles displayed in the Featured Tab of the Today Module on the Yahoo! Front Page during the first ten days in May 2009 \cite{yahoo}, to see how well they performed on real data.
	\item To empirically evaluate our implementations, we ran experiments similar to those in \cite{DBLP:journals/corr/JosephKMNR16} with randomly-drawn contexts. 
	\item We compiled our findings into a written report.
\end{enumerate}

@@

All algorithms and code were written using Python 3, along with numpy, SciPy, and various other Python libraries.

@@

The \texttt{TopInterval} learning algorithm was implemented true to form as presented in \cite{DBLP:journals/corr/JosephKMNR16}. Particular details of note - to ensure that all matrices used in computation were nonsingular, the first $d$ rounds are always chosen to be exploration rounds, where $d$ is the number of features.

@@

The implementation for \texttt{IntervalChaining} was simple given \texttt{TopInterval}, as it sufficed to alter the strategy for picking arms in each round to that of picking uniformly at random from the chain containing the top interval.

@@

\section{Yahoo! Dataset}
